### 2024-06-20 Paper/MSEPM-Manuscript.tex
Update MSEPM-Manuscript.tex
minor changes for distribution explanation

We simulated individuals whose methylation is determined by four factors and their associated epigenetic factors: 
a uniform factor approximating age with a non-linear association with methylation status 
$$q \sim\mathcal{U}(0,100), s_{Age}=q^{0.5}, \text{Figure 1A-B}$$ a binary trait resembling sex, linearly associated 
with methylation status $$q \sim B(1,.5), s_{Sex}=q, \text{Figure 1C-D}$$ a continuous normal (CN) phenotype 
resembling a cell type with a linear association with methylation status $$q \sim\mathcal{N}(1, 0.1), s_{CN}=q, 
\text{Figure 1E-F}$$ and a 
continuous exponentially (CE) distributed trait resembling obesity with a linear association with methylation status 
$$q \sim \frac{1}{20}e^{-x/20}, s_{CE}=q, \text{Figure 1G-H})$$

>>>>

We simulated individuals whose methylation is determined by four factors and their associated epigenetic factors: 
a uniformly distributed factor approximating age with a non-linear association with methylation status 
$$q \sim\mathcal{U}(0,100), s_{Age}=q^{0.5}, \text{Figure 1A-B}$$ a binary distributed trait resembling sex, linearly associated 
with methylation status $$q \sim B(1,.5), s_{Sex}=q, \text{Figure 1C-D}$$ a continuous normal (CN) phenotype 
resembling a cell type with a linear association with methylation status $$q \sim\mathcal{N}(1, 0.1), s_{CN}=q, 
\text{Figure 1E-F}$$ and a 
continuous exponentially (CE) distributed trait resembling obesity with a linear association with methylation status 
$$q \sim \frac{1}{20}e^{-x/20}, s_{CE}=q, \text{Figure 1G-H})$$
